\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-02-24 papers/itsc_2012/draft2.tex
re-did arch diagram in a dumb uml program
UI draws agents between lane lines

\pix{architecture.pdf}{An illustration of AORTA's components.}{scale=0.3}

@@

The map also has a geometric interpretation, used for visualization and physical
distances. A road has a sequence of points giving the line segments of the
center yellow line. These points could also be interpreted as control points for
a curved road, but AORTA uses straight lines as an approximation. Lanes are
physically placed a lane's width away from and parallel to the center line. (In
the case of one-ways, there is no center line; instead, the lanes simply cluster
around the invisible center lane, all pointing the same way.) Turns are modeled
with a single straight line connecting the end of one edge to the start of
another (so right turns often have $0$ length).

>>>>

\pix{architecture.png}
    {An illustration of AORTA's components.}
    {scale=0.2}

@@

The map also has a geometric interpretation, used for visualization and physical
distances. A road has a sequence of points giving the line segments of the
center yellow line. These points could also be interpreted as control points for
a curved road, but AORTA uses straight lines as an approximation. Lanes are
parallel to the center line, some width apart from one another.  Turns are
modeled with a single straight line connecting the end of one edge to the start
of another (so right turns often have $0$ length).
